% Abstract
\newpage
\thispagestyle{plain}
\begin{center}
{\Large \textbf{ABSTRACT}}
\end{center}
\vspace{1cm}

Electronic voting systems face core security challenges in simultaneously providing ballot privacy, vote integrity, voter anonymity, coercion resistance, and verifiability. Existing blockchain-based e-voting solutions address only subsets of these requirements, leaving critical gaps in coercion resistance and post-quantum security. This thesis presents a blockchain-based e-voting framework that integrates a multi-protocol cryptographic stack into a unified voting pipeline: Paillier homomorphic encryption with Helios-style CDS zero-knowledge proofs taken directly on the ciphertexts for vote validity, Pedersen commitments for Self-Masking Deniable Credential (SMDC) slot weights, linkable ring signatures for anonymous ballot submission, Samplable Anonymous Aggregation (SA\textsuperscript{2}) for two-server vote privacy, Kyber-768 for post-quantum hybrid encryption, and Damg\aa rd--Jurik--Nielsen threshold decryption for distributed key management.

The novel SMDC mechanism issues $k=5$ slot commitments per voter (1~real, 4~fake) and keys the real-slot index by a server-held HMAC secret that is disclosed to the legitimate voter only through a duress-bound reveal endpoint, gated on a registered behavioural signal. Together with a silent-discard short-circuit at cast time, these mechanisms provide coercion resistance against registration-time, post-registration, and cast-time coercers in practical blockchain voting contexts.

The system is implemented in approximately 20{,}000 lines of Go and deployed on Hyperledger Fabric v2.5. Performance evaluation confirms an $O(N \cdot m)$ total tally complexity ($O(N)$ per candidate) with a constant per-vote per-candidate cost of approximately 6.1~$\mu$s, empirically validated from 100 to 100{,}000 voters. The complete cast pipeline reaches a per-vote primitive floor of 68.3~ms (with registration-time Pedersen and SMDC issuance amortised across all of a voter's casts), and Hyperledger Caliper benchmarks of the deployed chaincode achieve approximately 200~TPS with 100\% success at 10{,}000 transactions. Thirteen end-to-end election simulations spanning 100 to 100{,}000 voters and both blockchain modes confirm 100\% tally integrity with a tight 81--111~ms per-vote latency band.

Compared with prior work, the proposed framework reduces the asymptotic tally cost from $O(N \cdot m^{2})$ (ISE-Voting) to $O(N \cdot m)$ --- a factor-$m$ improvement --- replaces BP-Vot's $\geq 98\%$ differential-privacy approximation with 100\% exact integer tallies, and adds post-quantum protection at only 5.35~ms per vote ($\approx 7.8\%$ of the per-vote primitive floor) via the Kyber-768 hybrid encryption layer. No surveyed prior framework combines this set of security properties with a Caliper-benchmarked Hyperledger Fabric deployment in a single architecture.

\vspace{1cm}

\noindent
\textbf{Keywords:} blockchain, e-voting, homomorphic encryption, zero-knowledge proofs, ring signatures, coercion resistance, post-quantum cryptography, Hyperledger Fabric, deniable credentials, anonymous aggregation
